Table compiler

### 2017-12-06 analyses/05-table-compiler.Rmd
Add new table compiler

---
title: "Table compiler"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 6
---

@@

## Data set table

```{r}
## Column names
colnames <- c("Group", "# taxa", "# characters", "Age range (MYA)", "Mass extinction (MYA)", "Reference(s)")

## Dataset names
dataset <- unlist(slugs)
dataset[4] <- "Heath2016"

## Groups
group <- c("eutherian mammals", "theropods", "theropods", "crinoids")

@@

## Mass extinction
mass <- c("66", "66", "66", "443")

@@

## Formatting the table
table_out <- data.frame(group, ntaxa, mcharacters, age_ranges, mass, reference)
colnames(table_out) <- colnames
rownames(table_out) <- dataset

>>>>

---
title: "Table compiler"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

## Data set table (Table 1)

```{r}
## Column names
rownames <- c("Group", "# taxa", "# characters", "Age range (MYA)", "Mass extinction (MYA)", "Reference(s)")

## Dataset names
dataset <- unlist(slugs)

## Groups
group <- c("mammals", "theropods", "theropods", "crinoids")

@@

## Mass extinction
mass <- c("66 (K-Pg)", "66 (K-Pg)", "66 (K-Pg)", "443 (O-S)")

@@

## Formatting the table
table_out <- data.frame(group, ntaxa, mcharacters, age_ranges, mass, reference)
table_out <- t(table_out)
colnames(table_out) <- dataset
rownames(table_out) <- rownames
